---
title: "Homework #1 -- Pet Names Dataset"
author: "Afrah jaber"
date: "`r Sys.Date()`"
output: github_document
---

**Student ID:2201002977

**Deadline:** 23:59 on Saturday, 13 February 2021

**Total Points:** 30


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises According to the data dictionary, how many pets are included in this dataset? 
- 52519

`1.

(4 points)
```{r}

```
#Exercises 2 how many varibles do we have for each pet?  
- variables 7



`2.

(4 points)

```{r}

```
Write your narrative below


`3. Copy the code provided in the homework documentation and paste it here. 
>seattlepets %>% 
+ count(animal_name, sort = TRUE)


(4 points)

```{r}

```
Write your narrative here

seattlepets %>%
  group_by(species) %>%
  count(animal_name, sort = TRUE) %>%
  slice_max(n, n = 5)

`4.

(10 points)

```{r species-name-top5, eval=TRUE}

```

`5.  What names are more common for cats than dogs? The ones above the line or the ones below the line? Oliver 
Answer here

Oliver and lily

(4 points)

`6. Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

Answer herer
If the names of the dogs increased, the names of the cats increased, and if the names of the dogs decreased, the names of the cats also decreased
(4 points)